A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-03-07 writeup/paper.tex
Analysis of performance within region v out of region

We performed an analysis of our data to address the following questions:
\begin{itemize}
\item How quickly can we expect work to be completed in a particular language? 
\item What is the quality of crowdsourced translations without quality control versus with it? 
\item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
\end{itemize}

@@

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure*}[h]
\centering
%\includegraphics[height=\linewidth,angle=270]{figures/completiontime-series}
\includegraphics[width=6in]{figures/completiontime-series}
\caption{Time (in days) to complete the translation HITs for 40 of the languages in our study. Tick marks represent the completion of individual assignments. Urdu and Russian were the first languages to be launched, followed by the others 2 days later. The languages which completed in the shortest amount of time were 4 Indian languages and Macedonian.}
%\caption{Time (in days) to complete all HITs in each language. Red bars show time until first HIT was started,
% relative to the time the first HIT in each language was started, relative to the time the first HIT in any language was started (first HIT started across all languages was Urdu). 
% blue bars show time until all HITs in each language were completed.}
\label{completion-time}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

We performed an analysis of our data to address the following questions, among others:
\begin{itemize}
\item How quickly can we expect work to be completed in a particular language? 
\item What is the quality of crowdsourced translations without quality control versus with it? 
\item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
\end{itemize}

%%%%%%%%%%%%%%% COMPLETION TIME CHART %%%%%%%%%%%
\begin{figure}[h]
\centering
%\includegraphics[height=\linewidth,angle=270]{figures/completiontime-series}
\includegraphics[height=\linewidth,angle=270]{figures/completiontime-series}
\caption{Days to complete the translation HITs for 40 of the languages. Tick marks represent the completion of individual assignments. }
\label{completion-time}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Speed of completion}

Figure \ref{completion-time} gives the completion times for 40 languages.  
Urdu and Russian were the first languages to be launched, followed by the others 2 days later. The 10 languages to finish in the shortest amount of time were: Tamil, Malayalam, Telugu, Hindi, Macedonian, Spanish, Serbian, Romanian, Gujarati, and Marathi. 7 of the 10 fastest languages are from India, which is unsurprising given the geographic distribution of workers.  Some languages follow the pattern of having a smattering of assignments completed early, with the rate picking up later.

\paragraph{Agreement with controls}

\paragraph{Performance within region}

We measured the average quality of workers who were in countries that plausibly speak a language, versus workers from countries that did not have large speaker populations of that language.  We used the Ethnologue \cite{ethnologue} to compile the list of countries for each language.  Table \ref{language-regions} reports the average translation quality of Turkers in countries with plausibly large speaker populations of each language, compared to the average quality of Turkers from outside the expected region for that language.

@@

### 2013-03-07 writeup/summary.tex
Analysis of performance within region v out of region

\begin{figure}[h]
\footnotesize
\begin{tabular}{lccl}
\multicolumn{4}{c}{Number of turkers per language}\\
\hline\hline
&\multicolumn{2}{c}{Avg. turker quality (\# Turkers)}&Primary locations\\
&In region&Out of region&of turkers in region\\
\hline\hline
Hindi&\textbf{0.54} (299)&0.47 (63)&India (285) UAE (5) UK (5) \\
Tamil&\textbf{0.55} (278)&0.54 (26)&India (271) US (3) Canada (2) \\
Malayalam&0.48 (235) &\textbf{0.55} (49)&India (224) UAE (6) US (3) \\
Spanish&\textbf{0.27} (205)&0.27 (39)&US (131) Mexico (18) Spain (14) \\
French&0.29 (183) &\textbf{0.31} (34)&India (68) US (48) France (25) \\
German&\textbf{0.35} (99)&0.31 (71)&Germany (51) US (29) Austria (9) \\
Italian&\textbf{0.32} (98)&0.27 (68)&Italy (44) US (32) Romania (9) \\
Chinese&\textbf{0.42} (123)&0.41 (28)&US (80) Singapore (15) China (14) \\
Telugu&\textbf{0.48} (102)&0.41 (35)&India (98) US (3) UAE (1) \\
Malay&\textbf{0.30} (15)&0.28 (116)&Malaysia (8) Singapore (4) US (2) \\
Turkish&\textbf{0.30} (83)&0.27 (47)&Turkey (39) US (20) Macedonia (12) \\
Kannada&0.64 (106) &\textbf{0.65} (21)&India (106) US (1) \\
Portuguese&0.20 (107) &\textbf{0.24} (19)&Brazil (46) Portugal (32) US (15) \\
Arabic&0.45 (62) &\textbf{0.45} (64)&Egypt (19) Jordan (17) Morocco (9) \\
Romanian&0.29 (87) &\textbf{0.33} (37)&Romania (77) US (6) Moldova (3) \\
Swedish&\textbf{0.30} (58)&0.29 (66)&US (28) Sweden (23) Finland (3) \\
Czech&0.24 (52) &\textbf{0.25} (71)&US (19) Czechrepublic (15) Serbia (5) \\
Irish&\textbf{0.32} (58)&0.26 (64)&US (41) Ireland (13) UK (4) \\
Amharic&0.21 (17) &\textbf{0.42} (105)&US (14) Ethiopia (3) \\
Russian&0.15 (72) &\textbf{0.16} (49)&US (38) Russia (8) Moldova (7) \\
\hline\hline
\end{tabular}
\end{figure}

>>>>

\begin{table*}
\scriptsize
%\footnotesize
\begin{center}
\begin{tabular}{lllll}
\hline\hline
&\multicolumn{2}{c}{Avg. quality (\# Turkers)}&Primary locations&Primary locations\\
&In region&Outside&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi&\textbf{0.35} (299)&0.29 (7)&India (285) UAE (5) UK (5) &Saudi Arabia (2) Russia (1) Oman (1) \\
Tamil&\textbf{0.39} (278)&0.00 (2)&India (271) US (3) Canada (2) &Tunisia (1) Egypt (1) \\
Malayalam&0.44 (235) &\textbf{0.56} (2)&India (224) UAE (6) US (3) &Saudi Arabia (1) Maldives (1) \\
Spanish&\textbf{0.71} (205)&0.60 (23)&US (131) Mexico (18) Spain (14) &India (19) Macedonia (2) New Zealand (1) \\
French&0.61 (183) &\textbf{0.80} (13)&India (68) US (48) France (25) &Greece (3) Japan (2) Netherlands (1) \\
German&\textbf{0.80} (99)&0.56 (58)&Germany (51) US (29) Austria (9) &India (47) Greece (2) UK (2) \\
Italian&\textbf{0.79} (98)&0.67 (51)&Italy (44) US (32) Romania (9) &India (38) Macedonia (2) Ireland (2) \\
Chinese&\textbf{0.22} (121)&0.18 (19)&US (79) Singapore (15) China (14) &Hongkong (6) Australia (3) Germany (2) \\
Malay&\textbf{0.76} (15)&0.72 (110)&Malaysia (8) Singapore (4) US (2) &India (106) Brunei (2) Australia (1) \\
Irish&0.61 (58) &\textbf{0.62} (59)&US (41) Ireland (13) UK (4) &India (45) Macedonia (5) Romania (5) \\
Czech&\textbf{0.70} (52)&0.62 (64)&US (19) Czech Republic (15) Serbia (5) &Macedonia (30) India (15) UK (5) \\
Turkish&\textbf{0.70} (83)&0.62 (32)&Turkey (39) US (20) Macedonia (12) &India (23) Pakistan (5) Taiwan (1) \\
Amharic&\textbf{0.17} (17)&0.02 (98)&US (14) Ethiopia (3) &India (69) Georgia (9) Macedonia (5) \\
Swedish&\textbf{0.64} (58)&0.57 (56)&US (28) Sweden (23) Finland (3) &India (26) Macedonia (10) Croatia (3) \\
Portuguese&\textbf{0.75} (107)&0.62 (4)&Brazil (46) Portugal (32) US (15) &Pakistan (1) Romania (1) Japan (1) \\
Arabic&0.21 (62) &\textbf{0.26} (48)&Egypt (19) Jordan (17) Morocco (9) &US (20) India (11) Algeria (4) \\
Kannada&\textbf{0.24} (106)&0.10 (1)&India (106) US (1) &France (1) Germany (1) \\
Russian&\textbf{0.33} (72)&0.26 (33)&US (38) Russia (8) Moldova (7) &India (17) Macedonia (4) UK (4) \\
Afrikaans&\textbf{0.73} (4)&0.64 (98)&South Africa (4) &India (93) Netherlands (2) UAE (1) \\
Sindhi&\textbf{0.16} (93)&0.11 (8)&India (55) Pakistan (37) US (1) &Macedonia (4) Georgia (2) Netherlands (1) \\
\hline\hline
\end{tabular}
\end{center}
\normalsize
\caption{The average translation quality of Turkers within a countries with larger speaker populations of a language versus Turkers from countries without large speaker populations of that language. }\label{language-regions}
\end{table*}
